Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
refactor future work

@@

@@

\subsection{Solutions For The Problem}

There are two viable approaches to overcome this challenge.
It is either necessary to enhance the Comparator while continuing
to utilize the state-of-the-art solver,
or it is possible to re-design the solver algorithm and create one
specifically designed to operate with noisier data.

\subsubsection{Improve The Comparator}

\subsubsection{Improving The Solver Algorithm}

The puzzle dilemma is a ``multiobjective optimization problem'',
where one objective is optimizing the time complexity,
and the other is optimizing the accuracy of the algorithm
in the presence of corrupted data.
All the major algorithms proposed up to this point have prioritize speed.
However, it is conceivable, and even probable,
that an algorithm prioritizing accuracy over speed could prove
effective with our comparator

\subsubsection{The Path Forward}

Improving the comparator is likely the most effective long-term solution,
but it presents a significant challenge: manually testing if certain
pieces fit together, followed by scanning and labeling,
is a time-intensive process that could require hundreds,
if not thousands, of hours.

On the other hand, improving the solver may not be the optimal long-term
solution, as it is likely to result in a worse time complexity.
However, it could yield significant short-term benefits.

Notably, this approach does not necessitate the creation of an extensive dataset
and has the potential to facilitate its development.
In fact, it could have the capability to solve numerous small
puzzles and subsequently auto-label the connections
based on the solutions it generates.

Given the two options, it has been decided to focus on improving
the solver algorithm. This choice was driven by the belief
that creating a new algorithm, and subsequently using it to
generate a dataset, would still be a more time-efficient
approach compared to manually constructing a dataset.

\section{The Labeling tool}
When the program runs, it also exports files that could be utilized
in the future for training a machine-learning-based comparator.
This section will list the available data and explain the format employed.

\subsection{Basic notions}

@@

\subsection{Image of each piece}

@@

\subsection{Image of each side}

@@

\subsection{Corners of each piece}
The file corners.json will be generated inside the folder results.
This file will contain a list of pieces.
Each piece has 4 sides, and each side has the coordinates of the two points
that delimit itself.\newline
An example of the generated json can be seen below.

@@

\subsection{Match for each side}
The file connections\_result.json will be generated
inside the folder results. This file will contain a list of pieces,
each piece has 4 sides, and each side has a link to the side of the piece
that matches it. The link can be null if the side is along the border.\newline
An example of the generated json can be seen below.

@@

\section{ConclusionsOld}
In conclusion, this paper has successfully achieved its objectives.
It has provided a comprehensive explanation of why real-world puzzles
present greater challenges compared to their digital counterparts.
Additionally, it has been shown that the same algorithm can have drastically worse
performance when working with real-world puzzles compared to digital ones.

>>>>

Until now this paper has not painted a positive picture about real-world
puzzle solving. The current digital puzzle solver achieves a good time
complexity, but requires really precise input data that we didn't manage
to achieve with our real-world comparator (\cref{document:my_comparator}).
On the other hand we managed to create a Solver (\cref{document:my_solver})
that could operate with the noisy data generated by our comparator;
But the greater reliability came at the expense of time complexity,
and this meant that the maximum size of puzzle that could be solved was limited.

Despite this inconvenience we think there is still a chance to solve
the problem by significantly improving the comparator.

@@

But this presents a significant challenge: manually testing if certain
pieces fit together, followed by scanning them and labeling,
is a time-intensive process that could require hundreds,
if not thousands, of hours.

However we just created a puzzle solver, even with a suboptimal
time complexity, can easily solve small size real world puzzles.
We could use it to solve a couple hundred small size puzzles,
and automatically label the results for us,
paving the way to a superior machine learning based comparator.

@@

To facilitate ours or someone else's future attempt to create a 
machine-learning-based comparator;
We added to our program the capability to export the data useful
to train a machine learning model.
This section will explain the format of the data.

\paragraph {Basic notions}

@@

\paragraph {Image of each piece}

@@

\paragraph {Image of each side}

@@

\paragraph{Corners of each piece}
The file corners.json will be generated inside the folder results.
This file will contain a list of pieces.
Each piece has 4 sides, and each side has the coordinates of the two points
that delimit itself.\newline
An example of the generated json can be seen below.

@@

\paragraph{Match for each side}
The file connections\_result.json will be generated
inside the folder results. This file will contain a list of pieces,
each piece has 4 sides, and each side has a link to the side of the piece
that matches it. The link can be null if the side is along the border.\newline
An example of the generated json can be seen below.

@@

In conclusion, this paper has successfully achieved its objectives.
It has provided a comprehensive explanation of why real-world puzzles
present greater challenges compared to their digital counterparts.
Additionally, it has been shown that the same algorithm can have drastically worse
performance when working with real-world puzzles compared to digital ones.
